### 2015-09-10 paper.tex
Add test matrix section names and descriptions

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied.

\todo[inline]{Add all test matrix sections and their descriptions here.}

>>>>

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are given below, which outline the
experimental data and code repository \cite{Bachant2015-RM2-data}.

\begin{itemize}

    \item \texttt{Perf-\{speed\}}: Performance curve at \texttt{\{speed\}} m/s
    tow speed, performed for (0.4, 0.6, 0.8, 1.0, 1.2) m/s.

    \item \texttt{Perf-\{speed\}-b}: Second performance curve at
    \texttt{\{speed\}} m/s, performed for the same tow speeds as above for
    reduced statistical uncertainty.

    \item \texttt{Perf-1.0-covers}: Performance curve at 1.0 m/s tow speed with
    cylindrical strut covers.

    \item \texttt{Perf-1.0-no-blades-covers}: Performance curve at 1.0 m/s with
    no blades and cylindrical strut covers.

    \item \texttt{Perf-1.0-no-blades}: Performance curve at 1.0 m/s with no
    blades (NACA 0021 struts only).

    \item \texttt{Perf-tsr\_0}: Performance at $\lambda=3.1$ for multiple tow
    speeds.

    \item \texttt{Perf-tsr\_0-b}: Additional set of runs duplicating the
    \texttt{Perf-tsr\_0} parameters.

    \item \texttt{Strut-torque-covers}: Measuring parasitic torque from
    cylindrical struts without towing.

    \item \texttt{Strut-torque}: Measuring parasitic torque from
    NACA 0021 struts without towing.

    \item \texttt{Tare-drag}: Drag on the turbine frame measured with the turbine
    removed.

    \item \texttt{Tare-torque}: Measurements of friction torque in shaft
    bearings for a range of RPMs used in the experiments.

    \item \texttt{Wake-\{speed\}-\{z/H\}}: Cross-stream wake profile at 1 m
    downstream ($x/D=0.93$), $\lambda=3.1$, \texttt{\{speed\}} m/s tow speed,
    and \texttt{\{z/H\}} vertical location.
\end{itemize}
